---
title: "Morans-I-and-GWR"
author: "Franklin"
date: "18/08/2021"
output: html_document
---

```{r,eval=FALSE}
# environment prepare
library(tidyverse)
library(data.table)
library(sp)
library(sf)
library(table1)
library(tm)
library(spatstat)
library(here)
library(sp)
library(rgeos)
# library(maptools)
library(tmap)
library(sf)
library(geojson)
library(geojsonio)
library(tmaptools)
library(RColorBrewer)
library(spdep) 
library(lubridate)
```


# Data Read

1.the index dataset
```{r}
# read data in R
raw_data = read.csv(here::here("Dataset","df_hh_EnR_ttwaName_asset_not_drop.csv"))

# you can have a overview of this dataset
print("The number of rows is: ")
nrow(raw_data)
print("The number of columns is: ")
ncol(raw_data)
print("70 of all varriables are:")
head(names(raw_data),n = 70)
```

2. spatial dataset
```{r}
# import spatial dataset

eng_ttwa = st_read(here::here("Dataset","Spatial","eng_ttwa_boundary.geojson"))

# plot the map
plot(st_geometry(eng_ttwa))
```

try to merge, but not a spatial type
```{r}
dfm = merge(raw_data,eng_ttwa,by.x="ttwa_code",by.y="TTWA11CD",all = TRUE)
```

# Data Prepare

```{r}
# select year
df_1998 = raw_data %>% filter(year==1998)
df_2008 = raw_data %>% filter(year==2008)
df_2018 = raw_data %>% filter(year==2018)
# df_2017_2018 = raw_data %>% filter(year==2017 | year==2018)

# merge
dfm_1998 = merge(eng_ttwa,df_1998,by.x="TTWA11CD",by.y="ttwa_code",all.x = TRUE)
dfm_2008 = merge(eng_ttwa,df_2008,by.x="TTWA11CD",by.y="ttwa_code",all.x = TRUE)
dfm_2018 = merge(eng_ttwa,df_2018,by.x="TTWA11CD",by.y="ttwa_code",all.x = TRUE)
# dfm_2017_2018 = merge(eng_ttwa,df_2017_2018,by.x="TTWA11CD",by.y="ttwa_code",all.x = TRUE)
dfm_all = merge(eng_ttwa,raw_data,by.x="TTWA11CD",by.y="ttwa_code",all.x = TRUE)

# n/a -> 0
dfm_1998 = dfm_1998 %>% replace_na(list(entry_rate=0,hh=0,average_assets=0))
dfm_2008 = dfm_2008 %>% replace_na(list(entry_rate=0,hh=0,average_assets=0))
dfm_2018 = dfm_2018 %>% replace_na(list(entry_rate=0,hh=0,average_assets=0))
# dfm_2017_2018 = dfm_2017_2018 %>% replace_na(list(entry_rate=0,hh=0,average_assets=0))
dfm_all_dna = dfm_all %>% replace_na(list(entry_rate=0,hh=0,average_assets=0))

# projection
dfm_1998 = dfm_1998 %>% st_transform(.,27700)
dfm_2008 = dfm_2008 %>% st_transform(.,27700)
dfm_2018 = dfm_2018 %>% st_transform(.,27700)

```


```{r}

cus_break = c(0.00,0.007,0.01,0.013,0.03,0.035,0.077,0.12153,0.14,0.16,0.32)
# library(viridis)
tmap_mode("plot")
```
# Distributiom

```{r}
df = dfm_1998
map_var = "entry_rate"
spatial_var = "ttwa"
legend_name = "Entry Rate (1998)"
title_name = "The Distribution of the Entry Rate of the England Tech Clusters(ttwa) in 1998"

enR_1998_map = tm_shape( df )+ 
        tm_compass( north = 0,
              type = "4star",
              show.labels = TRUE,
              cardinal.directions = c("N", "E", "S", "W"),
              lwd = 1,
              position = c("left","center"),
              bg.color = NA,
              bg.alpha = NA,
              just = NA)+ 
        tm_scale_bar(position=c("left", "center")
                    )+ 
        tm_fill(col = map_var,
              palette = "BuPu", n = 12,
              breaks = cus_break, 
              title=legend_name,
              legend.hist = TRUE,
              legend.hist.position = c("left", "center")
              )+ 
        tm_layout(main.title = "",main.title.size = .85,
                 frame=FALSE,
                 legend.outside =TRUE,
                 legend.hist.width = 1.2,
                 legend.hist.height = .25 )+
        tm_borders(col = "#D2D2D2", lwd = .5, lty = "solid", alpha = NA)
        
enR_1998_map
```


```{r}
df = dfm_2008
map_var = "entry_rate"
spatial_var = "ttwa"
legend_name = "Entry Rate (2008)"
title_name = "The Distribution of the Entry Rate of the England Tech Clusters(ttwa) in 2008"


enR_2008_map = tm_shape( df )+ 
        tm_compass( north = 0,
              type = "4star",
              show.labels = TRUE,
              cardinal.directions = c("N", "E", "S", "W"),
              lwd = 1,
              position = c("left","center"),
              bg.color = NA,
              bg.alpha = NA,
              just = NA)+ 
        tm_scale_bar(position=c("left", "center")
                    )+ 
        tm_fill(col = map_var,
              palette = "BuPu", n = 12,
              breaks = cus_break, 
              title=legend_name,
              legend.hist = TRUE,
              legend.hist.position = c("left", "center")
              )+ 
        tm_layout(main.title = "",main.title.size = .85,
                 frame=FALSE,
                 legend.outside =TRUE,
                 legend.hist.width = 1.2,
                 legend.hist.height = .25 )+
        tm_borders(col = "#D2D2D2", lwd = .5, lty = "solid", alpha = NA)
        
enR_2008_map
```

```{r}
df = dfm_2018
map_var = "entry_rate"
spatial_var = "ttwa"
legend_name = "Entry Rate (2018)"
title_name = "The Distribution of the Entry Rate of the England Tech Clusters(ttwa) in 2018"


enR_2018_map = tm_shape( df )+ 
        tm_compass( north = 0,
              type = "4star",
              show.labels = TRUE,
              cardinal.directions = c("N", "E", "S", "W"),
              lwd = 1,
              position = c("left","center"),
              bg.color = NA,
              bg.alpha = NA,
              just = NA)+ 
        tm_scale_bar(position=c("left", "center")
                    )+ 
        tm_fill(col = map_var,
              palette = "BuPu", n = 12,
              breaks = cus_break, 
              title=legend_name,
              legend.hist = TRUE,
              legend.hist.position = c("left", "center")
              )+ 
        tm_layout(main.title = "",main.title.size = .85,
                 frame=FALSE,
                 legend.outside =TRUE,
                 legend.hist.width = 1.2,
                 legend.hist.height = .25 )+
        tm_borders(col = "#D2D2D2", lwd = .5, lty = "solid", alpha = NA)
        
enR_2018_map
```

```{r}
enR_tmap = tmap_arrange(enR_1998_map,enR_2008_map,enR_2018_map,ncol = 1)

enR_tmap

# enR_tmap %>% tmap_save(.,here("Img","map_entry_rate_1998_to_2018.png"),dpi = 300)
```

# Add the Density Variables (1998, 2008 & 2018)

```{r}
dfm_1998 = dfm_1998 %>% 
    mutate(area = st_area(geometry))%>%
    mutate(area_km = units::set_units(area,km^2))%>%
    mutate(density = firms / area_km)%>%
    select(TTWA11CD,ttwa,year,entry_rate,hh,average_assets,density,firms,area_km)

dfm_2008 = dfm_2008 %>% 
    mutate(area = st_area(geometry))%>%
    mutate(area_km = units::set_units(area,km^2))%>%
    mutate(density = firms / area_km)%>%
    select(TTWA11CD,ttwa,year,entry_rate,hh,average_assets,density,firms,area_km)

dfm_2018 = dfm_2018 %>% 
    mutate(area = st_area(geometry))%>%
    mutate(area_km = units::set_units(area,km^2))%>%
    mutate(density = firms / area_km)%>%
    select(TTWA11CD,ttwa,year,entry_rate,hh,average_assets,density,firms,area_km)

dfm_1998 = dfm_1998 %>% replace_na(list(density=0))
dfm_2008 = dfm_2008 %>% replace_na(list(density=0))
dfm_2018 = dfm_2018 %>% replace_na(list(density=0))
```

Output .geojson
```{r}
here()

dfm_1998 %>% st_transform(.,27700)
st_write(obj = dfm_1998, dsn = here("Dataset","Spatial","dfm_1998_for_st_trans.geojson"))

st_write(obj = dfm_2008, dsn = here("Dataset","Spatial","dfm_2008.geojson"))

st_write(obj = dfm_2018, dsn = here("Dataset","Spatial","dfm_2018.geojson"))
```


# Centroids and neighbour list

```{r}
# projection

dfm_1998 = dfm_1998 %>% st_transform(.,27700)
dfm_2008 = dfm_2008 %>% st_transform(.,27700)
dfm_2018 = dfm_2018 %>% st_transform(.,27700)

coordsW_1998 = dfm_1998%>%
   st_centroid()%>%
   st_geometry()

coordsW_2008 = dfm_2008%>%
   st_centroid()%>%
   st_geometry()

coordsW_2018 = dfm_2018%>%
   st_centroid()%>%
   st_geometry()

Ettwa_nb_1998 = dfm_1998 %>% 
  poly2nb(., queen=T)

Ettwa_nb_2008 = dfm_2008 %>% 
  poly2nb(., queen=T)

Ettwa_nb_2018 = dfm_2018 %>% 
  poly2nb(., queen=T)

df = dfm_2018
coordsW = coordsW_2018
nb = Ettwa_nb_2018

plot(df$geometry)
plot(nb,coordsW,col="blue",add=T)

# plot(coordsW,axes=TRUE)
```

```{r}
#Create a spatial weights object from these weights
Ettwa_1998.wl = nb2listw(Ettwa_nb_1998, style="W",zero.policy = TRUE)

Ettwa_2008.wl = nb2listw(Ettwa_nb_2008, style="W",zero.policy = TRUE)

Ettwa_2018.wl = nb2listw(Ettwa_nb_2018, style="W",zero.policy = TRUE)
```

# Spatial autocorrelation: Global Moran'I Index

## Global Moran's Index

In order to calculate the three time periods global Moran's I 

1.  Morans'I in entry rate in 1998
```{r}
I_Ettwa_enR_1998 = dfm_1998 %>%
  pull(entry_rate) %>% 
  as.vector() %>% 
  moran.test(.,Ettwa_1998.wl,zero.policy = TRUE)

I_Ettwa_enR_2008 = dfm_2008 %>%
  pull(entry_rate) %>% 
  as.vector() %>% 
  moran.test(.,Ettwa_2008.wl,zero.policy = TRUE)

I_Ettwa_enR_2018 = dfm_2018 %>%
  pull(entry_rate) %>% 
  as.vector() %>% 
  moran.test(.,Ettwa_2018.wl,zero.policy = TRUE)

```

2. Morans'I in entry rate in 2008
```{r}
I_Ettwa_enR_1998 %>%  head()
print("---------------------------------------------------------------")
head(I_Ettwa_enR_2008)
print("---------------------------------------------------------------")
head(I_Ettwa_enR_2018)
```

```{r}
I_Ettwa_den_1998 = dfm_1998 %>%
  pull(density) %>% 
  as.vector() %>% 
  moran.test(.,Ettwa_1998.wl,zero.policy = TRUE)

I_Ettwa_den_2008 = dfm_2008 %>%
  pull(density) %>% 
  as.vector() %>% 
  moran.test(.,Ettwa_2008.wl,zero.policy = TRUE)

I_Ettwa_den_2018 = dfm_2018 %>%
  pull(density) %>% 
  as.vector() %>% 
  moran.test(.,Ettwa_2018.wl,zero.policy = TRUE)

head(I_Ettwa_den_1998)
print("---------------------------------------------------------------")
head(I_Ettwa_den_2008)
print("---------------------------------------------------------------")
head(I_Ettwa_den_2018)

```

Table 2 Spatio-temporal dynamics cluster analysis

|Year| Moran's Index|p value|z-score|
|----|:------:| :---:|---:|
|1998 |  0.118|  0.00 |2.4385
|2008 |  0.062|  0.08 |1.3483
|2018 |  0.056|  0.10 |1.2382   

Table 3 Spatio-temporal density cluster analysis

|Year| Moran's Index|p value|z-score|
|----|:------:| :---:|---:|
|1998 0.4359|  0.00 | 10.07783
|2008 |  0.3248|  0.00 | 7.54488
|2018 |  0.1891|  0.00| 4.982051

## Global G test

Getis Ord General G…? This tells us whether high or low values are clustering. If **G > Expected = High values clustering**; if **G < expected = low values clustering**
```{r}

# take 1998 for example
G_Ettwa_Global_enR = dfm_1998 %>%
  pull(entry_rate) %>%
  as.vector()%>%
  globalG.test(., Ettwa_1998.wl,zero.policy = T)

G_Ettwa_Global_enR

```
This condition: G > E = high values means that high values tending to clustering in 1998

## Local Moran's Index

### Data Process
```{r}
# entry rate
I_Ettwa_Local_enR_1998 =  dfm_1998 %>%
  pull(entry_rate) %>%
  as.vector()%>%
  localmoran(., Ettwa_1998.wl,zero.policy = T)%>%
  as_tibble()

I_Ettwa_Local_enR_2008 =  dfm_2008 %>%
  pull(entry_rate) %>%
  as.vector()%>%
  localmoran(., Ettwa_2008.wl,zero.policy = T)%>%
  as_tibble()

I_Ettwa_Local_enR_2018 =  dfm_2018 %>%
  pull(entry_rate) %>%
  as.vector()%>%
  localmoran(., Ettwa_2018.wl,zero.policy = T)%>%
  as_tibble()


# density
I_Ettwa_Local_den_1998 <- dfm_1998 %>%
  pull(density) %>%
  as.vector()%>%
  localmoran(., Ettwa_1998.wl,zero.policy = T)%>%
  as_tibble()

I_Ettwa_Local_den_2008 <- dfm_2008 %>%
  pull(density) %>%
  as.vector()%>%
  localmoran(., Ettwa_2008.wl,zero.policy = T)%>%
  as_tibble()

I_Ettwa_Local_den_2018 <- dfm_2018 %>%
  pull(density) %>%
  as.vector()%>%
  localmoran(., Ettwa_2018.wl,zero.policy = T)%>%
  as_tibble()


#what does the output (the localMoran object) look like?
slice_head(I_Ettwa_Local_den_1998, n=5)
```

add Local Moran's I Indicators
```{r}
dfm_1998 <- dfm_1998 %>%
  mutate(entry_rate_I = as.numeric(I_Ettwa_Local_enR_1998$Ii))%>%
  mutate(entry_rate_Iz =as.numeric(I_Ettwa_Local_enR_1998$Z.Ii))%>%
  mutate(density_I =as.numeric(I_Ettwa_Local_den_1998$Ii))%>%
  mutate(density_Iz =as.numeric(I_Ettwa_Local_den_1998$Z.Ii))

dfm_1998 = dfm_1998 %>%   
  replace_na(list(entry_rate_I=0,entry_rate_Iz=0,density_I=0,density_Iz=0))

dfm_2008 <- dfm_2008 %>%
  mutate(entry_rate_I = as.numeric(I_Ettwa_Local_enR_2008$Ii))%>%
  mutate(entry_rate_Iz =as.numeric(I_Ettwa_Local_enR_2008$Z.Ii))%>%
  mutate(density_I =as.numeric(I_Ettwa_Local_den_2008$Ii))%>%
  mutate(density_Iz =as.numeric(I_Ettwa_Local_den_2008$Z.Ii))

dfm_2008 = dfm_2008 %>%   
  replace_na(list(entry_rate_I=0,entry_rate_Iz=0,density_I=0,density_Iz=0))

dfm_2018 <- dfm_2018 %>%
  mutate(entry_rate_I = as.numeric(I_Ettwa_Local_enR_2018$Ii))%>%
  mutate(entry_rate_Iz =as.numeric(I_Ettwa_Local_enR_2018$Z.Ii))%>%
  mutate(density_I =as.numeric(I_Ettwa_Local_den_2018$Ii))%>%
  mutate(density_Iz =as.numeric(I_Ettwa_Local_den_2018$Z.Ii))

dfm_2018 = dfm_2018 %>%   
  replace_na(list(entry_rate_I=0,entry_rate_Iz=0,density_I=0,density_Iz=0))
```

### Map making for LISA

- data points >2.58 or <-2.58 standard deviations away from the mean are significant at the 99% level (<1% chance that autocorrelation not present);
- >1.96 - <2.58 or <-1.96 to >-2.58 standard deviations are significant at the 95% level (<5% change that autocorrelation not present).
- >1.65 = 90% etc.

```{r}
breaks1 = c(-1000,-2.58,-1.96,-1.65,1.65,1.96,2.58,1000)
MoranColours = rev(brewer.pal(8, "RdGy"))
```

```{r}
# breaks1 = c(-5,-1,-0.7,-0.5,-0.1,0.1,0.5,0.7,1,5)
breaks1<-c(-1000,-2.58,-1.96,-1.65,1.65,1.96,2.58,1000)
tmap_mode("plot")

df = dfm_1998 %>% st_transform(.,27700)
legend_name = "Local Moran's I (1998)"
title_name = ""
# title_name = "Entry Rate in Travel to Work Area in England"
#now plot on an interactive map
Iz_map_1998 = tm_shape(df) +
    tm_polygons("density_Iz",
        style="fixed",
        breaks=breaks1,
        palette=MoranColours,
        midpoint=NA,
        title=legend_name)+
      tm_compass( north = 0,
              type = "4star",
              show.labels = TRUE,
              cardinal.directions = c("N", "E", "S", "W"),
              lwd = 1,
              size = 2.5,
              position = c("right","top"),
              bg.color = NA,
              bg.alpha = NA,
              just = NA)+ 
    tm_scale_bar(position=c("right", "bottom"))+
    tm_layout(main.title = title_name,
              main.title.size = .85,
              legend.text.size = 0.5)

Iz_map_1998
```

```{r}
df = dfm_2008
legend_name = "Local Moran's I (2008)"
title_name = ""
# title_name = "Entry Rate in Travel to Work Area in England"
#now plot on an interactive map
Iz_map_2008 = tm_shape(df) +
    tm_polygons("density_Iz",
        style="fixed",
        breaks=breaks1,
        palette=MoranColours,
        midpoint=NA,
        title=legend_name)+
      tm_compass( north = 0,
              type = "4star",
              show.labels = TRUE,
              cardinal.directions = c("N", "E", "S", "W"),
              lwd = 1,
              size = 2.5,
              position = c("right","top"),
              bg.color = NA,
              bg.alpha = NA,
              just = NA)+ 
    tm_scale_bar(position=c("right", "bottom"))+
    tm_layout(main.title = title_name,
              main.title.size = .85,
              legend.text.size = 0.5)

Iz_map_2008
```

```{r}
df = dfm_2018
legend_name = "Local Moran's I (2018)"
title_name = ""
# title_name = "Entry Rate in Travel to Work Area in England"
#now plot on an interactive map
Iz_map_2018 = tm_shape(df) +
    tm_polygons("density_Iz",
        style="fixed",
        breaks=breaks1,
        palette=MoranColours,
        midpoint=NA,
        title=legend_name)+
      tm_compass( north = 0,
              type = "4star",
              show.labels = TRUE,
              cardinal.directions = c("N", "E", "S", "W"),
              lwd = 1,
              size = 2.5,
              position = c("right","top"),
              bg.color = NA,
              bg.alpha = NA,
              just = NA)+ 
    tm_scale_bar(position=c("right", "bottom"))+
    tm_layout(main.title = title_name,
              main.title.size = .85,
              legend.text.size = 0.5)

Iz_map_2018
```

```{r}
grid.newpage()
pushViewport(viewport(layout = grid.layout(
        nrow = 2,
        ncol = 3,
        heights = c(0.1, 0.9))))

grid.text("Entry Rate in Travel to Work Area in England", vp = viewport(layout.pos.row = 1, layout.pos.col = 1:3))
print(Iz_map_1998, vp = viewport(layout.pos.row = 2, layout.pos.col = 1))
print(Iz_map_2008, vp = viewport(layout.pos.row = 2, layout.pos.col = 2))
print(Iz_map_2018, vp = viewport(layout.pos.row = 2, layout.pos.col = 3))
```


## Gi-Score

### Data Process
calculate the Gi-Score
```{r}
# Gi-Score

# entry rate
G_Ettwa_Local_enR_1998 =  dfm_1998 %>%
  pull(entry_rate) %>%
  as.vector()%>%
  localG(., Ettwa_1998.wl,zero.policy = T)

G_Ettwa_Local_enR_2008 =  dfm_2008 %>%
  pull(entry_rate) %>%
  as.vector()%>%
  localG(., Ettwa_2008.wl,zero.policy = T)

G_Ettwa_Local_enR_2018 =  dfm_2018 %>%
  pull(entry_rate) %>%
  as.vector()%>%
  localG(., Ettwa_2018.wl,zero.policy = T)

# density
G_Ettwa_Local_den_1998 =  dfm_1998 %>%
  pull(density) %>%
  as.vector()%>%
  localG(., Ettwa_1998.wl,zero.policy = T)

G_Ettwa_Local_den_2008 =  dfm_2008 %>%
  pull(density) %>%
  as.vector()%>%
  localG(., Ettwa_2008.wl,zero.policy = T)

G_Ettwa_Local_den_2018 =  dfm_2018 %>%
  pull(density) %>%
  as.vector()%>%
  localG(., Ettwa_2018.wl,zero.policy = T)
```

add columns in dataset
```{r}
# entry rate
dfm_1998 = dfm_1998%>%
  mutate(entry_rate_G = as.numeric(G_Ettwa_Local_enR_1998))%>% 
  replace_na(list(entry_rate_G=0))

dfm_2008 = dfm_2008%>%
  mutate(entry_rate_G = as.numeric(G_Ettwa_Local_enR_2008))%>% 
  replace_na(list(entry_rate_G=0))

dfm_2018 = dfm_2018%>%
  mutate(entry_rate_G = as.numeric(G_Ettwa_Local_enR_2018))%>% 
  replace_na(list(entry_rate_G=0))

# density
dfm_1998 = dfm_1998%>%
  mutate(density_G = as.numeric(G_Ettwa_Local_den_1998))%>% 
  replace_na(list(density_G=0))

dfm_2008 = dfm_2008%>%
  mutate(density_G = as.numeric(G_Ettwa_Local_den_2008))%>% 
  replace_na(list(density_G=0))

dfm_2018 = dfm_2018%>%
  mutate(density_G = as.numeric(G_Ettwa_Local_den_2018))%>% 
  replace_na(list(density_G=0))
```

### Map making

This research set the breaks manually based on the rule that entry rate >2.58 or <-2.58 standard deviations away from the mean are significant at the 99% level (<1% chance that autocorrelation not present); >1.96 - <2.58 or <-1.96 to >-2.58 standard deviations are significant at the 95% level (<5% change that autocorrelation not present). >1.65 = 90% etc.
```{r}
# breaks1 = c(-5,-1,-0.7,-0.5,-0.1,0.1,0.5,0.7,1,5)
breaks1<-c(-1000,-2.58,-1.96,-1.65,1.65,1.96,2.58,1000)

tmap_mode("plot")
GIColours = rev(brewer.pal(8, "RdBu"))
df = dfm_1998  
legend_name = "Gi* (1998)"
title_name = ""
# title_name = "Entry Rate in Travel to Work Area in England"
#now plot on an interactive map
G_map_1998 = tm_shape(df) +
    tm_polygons("density_G",
        style="fixed",
        breaks=breaks1,
        palette=GIColours,
        midpoint=NA,
        title=legend_name)+
      tm_compass( north = 0,
              type = "4star",
              show.labels = TRUE,
              cardinal.directions = c("N", "E", "S", "W"),
              lwd = 1,
              size = 2.5,
              position = c("right","top"),
              bg.color = NA,
              bg.alpha = NA,
              just = NA)+ 
    tm_scale_bar(position=c("right", "bottom"))+
    tm_layout(main.title = title_name,
              main.title.size = .85,
              legend.text.size = 0.5)

G_map_1998
```


```{r}
df = dfm_2008
legend_name = "Gi* (2008)"
title_name = ""
# title_name = "Entry Rate in Travel to Work Area in England"
#now plot on an interactive map
G_map_2008 = tm_shape(df) +
    tm_polygons("density_G",
        style="fixed",
        breaks=breaks1,
        palette=GIColours,
        midpoint=NA,
        title=legend_name)+
      tm_compass( north = 0,
              type = "4star",
              show.labels = TRUE,
              cardinal.directions = c("N", "E", "S", "W"),
              lwd = 1,
              position = c("right","top"),
              bg.color = NA,
              bg.alpha = NA,
              size = 2.5,
              just = NA)+ 
    tm_scale_bar(position=c("right","bottom"))+
    tm_layout(main.title = title_name,
              main.title.size = .85,
              legend.text.size = 0.5)

G_map_2008
```

```{r}
df = dfm_2018
legend_name = "Gi* (2018)"
title_name = ""
# title_name = "Entry Rate in Travel to Work Area in England"
#now plot on an interactive map
G_map_2018 = tm_shape(df) +
    tm_polygons("density_G",
        style="fixed",
        breaks=breaks1,
        palette=GIColours,
        midpoint=NA,
        title=legend_name)+
      tm_compass( north = 0,
              type = "4star",
              show.labels = TRUE,
              cardinal.directions = c("N", "E", "S", "W"),
              lwd = 1,
              position = c("right","top"),
              bg.color = NA,
              bg.alpha = NA,
              size = 2.5,
              just = NA)+ 
    tm_scale_bar(position=c("right","bottom"))+
    tm_layout(main.title = title_name,
              main.title.size = .85,
              legend.text.size = 0.5)

G_map_2018
```

arrange the map
```{r}

grid.newpage()
pushViewport(viewport(layout = grid.layout(
        nrow = 2,
        ncol = 3,
        heights = c(0.1, 0.9))))
grid.text("Entry Rate in Travel to Work Area in England", vp = viewport(layout.pos.row = 1, layout.pos.col = 1:3))
print(G_map_1998, vp = viewport(layout.pos.row = 2, layout.pos.col = 1))
print(G_map_2008, vp = viewport(layout.pos.row = 2, layout.pos.col = 2))
print(G_map_2018, vp = viewport(layout.pos.row = 2, layout.pos.col = 3))

# tmap_save(here("Img","G_score_enR.png"),dpi=300)
# tmap_arrange(G_map_1998,G_map_2008,G_map_2018,nrow = 1)
```

```{r}
st_write(obj = dfm_1998, dsn = here("Dataset","Spatial","dfm_1998_output.geojson"))

st_write(obj = dfm_2008, dsn = here("Dataset","Spatial","dfm_2008_output.geojson"))

st_write(obj = dfm_2018, dsn = here("Dataset","Spatial","dfm_2018_output.geojson"))
```

```{r}
dfm_1998 %>% head(
)
```


# LISA TRY

```{r}
# neighbours2 <- poly2nb(dfm_1998, queen = FALSE)
# listw <- nb2listw(neighbours2,zero.policy = TRUE)
# listw
```


```{r}
neighbours2 <- poly2nb(dfm_2008, queen = FALSE)
listw = nb2listw(neighbours2, style = "W", zero.policy = TRUE)

local = I_Ettwa_Local_enR_1998
```


```{r}

tm_shape(dfm_1998) +
  tm_fill(col = "density_I",
          style = "quantile",
          title = "local moran statistic",
          midpoint = NA) 
```

```{r}
local$Z.Ii
```

```{r}
library(tidyverse)  # Modern data science workflow
library(sf)
library(sp)
library(spdep)
library(rgdal)
library(rgeos)
# library(tmap)
library(tmaptools)
library(spgwr)
library(grid)
library(gridExtra)

```

```{r}
quadrant <- vector(mode="numeric",length=nrow(local))

# centers the variable of interest around its mean
m.qualification <- (dfm_1998$density - mean(dfm_1998$density)) %>% as.vector()

# centers the local Moran's around the mean
m.local <- (local$Ii- mean(local$Ii))%>% as.vector()

# significance threshold
signif <- 0.1 

# builds a data quadrant
quadrant[m.qualification>0 & m.local>0] <- 4  
quadrant[m.qualification<0 & m.local<0] <- 1    
quadrant[m.qualification<0 & m.local>0] <- 2
quadrant[m.qualification>0 & m.local<0] <- 3
quadrant[local$Z.Ii>signif] <- 0 

# plot in r
brks <- c(0,1,2,3,4)
colors <- c("white","blue",rgb(0,0,1,alpha=0.4),rgb(1,0,0,alpha=0.4),"red")
plot(dfm_1998$density,border="lightgray",col=colors[findInterval(quadrant,brks,all.inside=FALSE)])
box()
legend("bottomleft", legend = c("insignificant","low-low","low-high","high-low","high-high"),fill=colors,bty="n")
```




# Study Area

```{r}
# study area

eng_ttwa = st_read(here::here("Dataset","Spatial","eng_ttwa_boundary.geojson"))

eng_ttwa = eng_ttwa

uk_ttwa = st_read(here::here("Dataset","Spatial","Travel_to_Work_Areas__December_2011__Generalised_Clipped_Boundaries_in_United_Kingdom.geojson"))

```

```{r}
title_name =  ""

tmap_options(check.and.fix = TRUE)

study_area = tm_shape(uk_ttwa) +
    tm_borders(alpha = 0.5, lwd = .15, lty = 1
        )+
    tm_fill(
        )+
    tm_shape(eng_ttwa)+
      tm_fill(col = "blue", 
            alpha = 0.3)+
      tm_borders(col = "blue", lwd = .25, lty = 1, alpha = 0.5)+
    tm_layout(main.title = title_name)+
    tm_compass( north = 0,
              type = "8star",
              show.labels = TRUE,
              cardinal.directions = c("N", "E", "S", "W"),
              lwd = 1,
              size = 2.5,
              position = c("left","top"),
              just = NA)+ 
    tm_scale_bar(position=c("right", "bottom"))

study_area
```



